Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-05 draft/accordionComplexSurfaces.tex
example double cycles

\vincent{TODO: surfaces double cycles.}
\end{example}

>>>>

The corresponding perfect matchings (see Remark~\ref{rem:propertiesSurface}) are empty since there is no blossom vertices.
Moreover, $\bar Q$ has~$1$ infinite straight walk when~$|Q_0|$ is odd and~$2$ when~$|Q_0|$ is even, and~$\bar Q\koszul$ always has~$2$ infinite straight walks.
Therefore, the corresponding surfaces have no boundary component and
\begin{itemize}
\item $3$ punctures and genus~$(|Q_0|-1)/2$ when~$|Q_0|$ is odd, and 
\item $4$ punctures and genus~$(|Q_0|-2)/2$ when~$|Q_0|$ is even.
\end{itemize}
The first few corresponding surfaces are represented in \fref{fig:doubleCyclesSurfaces}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{doubleCyclesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the double cycle quivers with~$3, 4, 5$ vertices.}
	\label{fig:doubleCyclesSurfaces}
\end{figure}
